### 2024-01-31 ms.qmd
Updates

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## A) L. delicata
deli <- fit_m(clean_df, "deli", refit = TRUE)
write.csv(deli, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich <- fit_m(clean_df, "guich", refit = TRUE)
write.csv(guich, file= "./output/Checking/guich.csv")
```

@@

  PValue = rep(pvalue, each = 1),

@@

@@

  pivot_wider(names_from = Task, values_from = c(Mean, `95% CI`, `p-value`)) %>% # to split between Asociative and Reversal

@@

write.csv(new_table_data, file= "./output/Checking/new_table_data.csv")

@@

real_table <- flextable(new_table_data) %>%
    bold(~ `p-value_Associative` < 0.05, ~ `p-value_Associative` + Mean_Associative + `95% CI_Associative`) %>%
    bold(~ `p-value_Reversal` < 0.05, ~ `p-value_Reversal` + Mean_Reversal + `95% CI_Reversal`) %>%

@@

    add_header_row(values = c("", "Associative task", "Reversal task"), colwidths = c(3, 3, 3)) %>%
    set_header_labels(Mean_Associative = "Mean",
                      `95% CI_Associative` = "95% CI",
                      `p-value_Associative` = "p-value",
                      Mean_Reversal = "Mean",
                      `95% CI_Reversal` = "95% CI",
                      `p-value_Reversal` = "p-value") %>%

@@

    flextable::compose(i = c(2:8,10:16), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    flextable::compose(i = c(2:4,6:8,10:12,14:16), j = 2, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the second column
    hline(i = c(4,12), j = c(2:9), part = "body") %>% # To make some horizontal lines
    hline(i = c(8), j = c(1:9), part = "body") %>% # To make some horizontal lines
    vline(i = (1:16), j = c(3,6), part = "body") %>% # To make some vertical lines on body
    vline(j=c(3,6), part = "header") %>% # To make some vertical lines on header

@@

We did not find any significant differences between treatments in _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((deli_ControlHot + drb_ControlHot) - (deli_CORTHot + drb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((deli_ControlHot + drb_ControlHot) - (deli_CORTHot + drb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((deli_ControlHot + drb_ControlHot) - (deli_ControlCold + drb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlHot + drb_ControlHot) - (deli_ControlCold + drb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((deli_CORTHot + drb_CORTHot) - (deli_CORTCold + drb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + drb_CORTHot) - (deli_CORTCold + drb_CORTCold)), 3)`) (see @Figdeli) or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean((guich_ControlCold + grb_ControlCold) - (guich_CORTCold + grb_CORTCold)), 3)`, p- value = `r format_dec(pmcmc((guich_ControlCold + grb_ControlCold) - (guich_CORTCold + grb_CORTCold)), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean((guich_ControlHot + grb_ControlHot) - (guich_CORTHot + grb_CORTHot)), 3)`, p- value = `r format_dec(pmcmc((guich_ControlHot + grb_ControlHot) - (guich_CORTHot + grb_CORTHot)), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean((guich_ControlHot + grb_ControlHot) - (guich_ControlCold + grb_ControlCold)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlHot + grb_ControlHot) - (guich_ControlCold + grb_ControlCold)), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean((guich_CORTHot + grb_CORTHot) - (guich_CORTCold + grb_CORTCold)), 3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + grb_CORTHot) - (guich_CORTCold + grb_CORTCold)), 3)`) (see @Figguich). We did not find any effect of incubation temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot + drb_CORTHot + drb_ControlHot) - (deli_CORTCold + deli_ControlCold + drb_CORTCold + drb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot + drb_CORTHot + drb_ControlHot) - (deli_CORTCold + deli_ControlCold + drb_CORTCold + drb_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot + grb_CORTHot + grb_ControlHot) -(guich_CORTCold + guich_ControlCold + grb_CORTCold + grb_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot + grb_CORTHot + grb_ControlHot) -(guich_CORTCold + guich_ControlCold + grb_CORTCold + grb_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot + drb_ControlCold + drb_ControlHot) - (deli_CORTCold + deli_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot + drb_ControlCold + drb_ControlHot) - (deli_CORTCold + deli_CORTHot + drb_CORTCold + drb_CORTHot)), 3)`;_L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot + grb_ControlCold + grb_ControlHot)-(guich_CORTCold + guich_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot + grb_ControlCold + grb_ControlHot)-(guich_CORTCold + guich_CORTHot + grb_CORTCold + grb_CORTHot)), 3)`) when groups were pooled. Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot + drb_CORTCold + drb_ControlCold + drb_CORTHot + drb_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot + grb_CORTCold + grb_ControlCold + grb_CORTHot + grb_ControlHot)), 3)`).

@@

Model formula for the reversal task is:  
Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)  
Plots for the different models of the associative task:  
1.- _L. delicata_  
  1.a.- Red  
```{r , plotmod_drr, out.width="70%", fig.align="center"}
plot(mod_drr)
```

@@

  1.b.- Blue  
```{r , plotmod_drb, out.width="70%", fig.align="center"}  
plot(mod_drb)
```

2.- _L. guichenoti_  
  2.a.- Red  
```{r , plotmod_grr, out.width="70%", fig.align="center"}
plot(mod_grr)
```

  2.b.- Blue  
```{r , plotmod_grb, out.width="70%", fig.align="center"}
plot(mod_grb)
```

>>>>

```{r, models}
#| label: models
# Fitting the model and extraction of posteriors for both types of task and species using fit_m function (see func.r in R folder). The result everytime the function is used is a df with the posteriors of the model. The functions saves the model automatically in output/models; and when the parameter refit = FALSE then the posteriors are extracted from the model previously written instead of fitting the model again each time.
source(here("R", "func.R"))
# Model formula: FC_reversal ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)
## A) L. delicata
deli <- fit_m(clean_df, "deli", refit = FALSE)
write.csv(deli, file= "./output/Checking/deli.csv")
## B) L. guichenoti
guich <- fit_m(clean_df, "guich", refit = FALSE)
write.csv(guich, file= "./output/Checking/guich.csv")
```

@@

  PValue = rep(pvalue, each = 1)

@@

write.csv(table_df, file= "./output/Checking/df.csv")

@@

@@

write.csv(new_table_df, file= "./output/Checking/new_table_data.csv")

@@

real_table <- flextable(new_table_df) %>%
    bold(~ `p-value` < 0.05, ~ `p-value` + Mean + `95% CI`) %>%

@@

    set_header_labels(Mean = "Mean",
                      `95% CI` = "95% CI",
                      `p-value` = "p-value") %>%

@@

    flextable::compose(i = c(2:4,6:8), j = 1, value = as_paragraph(""), part = "body") %>% # To remove some of the values in the first column
    hline(i = 4, j = c(1:5), part = "body") %>% # To make some horizontal lines

@@

We did not find any significant differences between treatments in _L. delicata_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_dec(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_dec(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L. guichenoti_ ('Control-Cold' - 'CORT-Cold' = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; 'Control-Hot' - 'CORT-Hot' = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; 'Control-Hot' - 'Control-Cold' = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_dec(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; 'CORT-Hot' - 'CORT-Cold' = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_dec(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results). We did not find any effect of incubation temperature (_L. delicata_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_dec(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L. guichenoti_: 'Hot' learning slope - 'Cold' learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_dec(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) or the hormone (_L. delicata_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`;_L. guichenoti_: 'Control' learning slope - 'CORT' learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_dec(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`) when groups were pooled. Finally, we did not find any significant differences when we compared the estimated slopes between species for the reversal task (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_dec(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).

@@

Model formula for the reversal task is:  
Choice  ~ trial_reversal*cort*temp + (1 + trial_reversal|lizard_id)  
Plots for the different models of the associative task:  
1.- _L. delicata_  
  1.a.- Red  
```{r , plotmod_drr, out.width="70%", fig.align="center"}
plot(mod_deli)
```

@@

2.- _L. guichenoti_  
```{r , plotmod_grr, out.width="70%", fig.align="center"}
plot(mod_guich)
```
